Plots_Genome

### 2024-03-27 Code/Plots_Genome.Rmd
Update Plots_Genome.Rmd

```{r, assign filepaths, include = FALSE}
DataIn <- file.path("..","Data", "CleanData")
Figures <- file.path("..", "Output", "Figures")
# BLAST <- file.path("..", "BLAST")
```

@@

```{r, ProchlorococcusEnzymeKms ggsave, include = FALSE} 
ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms.png"), plot = ProchlorococcusEnzymeKms, height = 23, width = 20)
```

@@

```{r, DNARepairFig ggsave, include = FALSE} 
ggsave(filename = file.path(Figures, "DNARepairFig.png"), plot = DNARepairFig, height =5 , width = 5)
ggsave(filename = file.path(Figures, "Fig12.tiff"), plot = DNARepairFig, height =5 , width = 5, compression = "lzw")
```

@@

```{r, save ProchlorococcusLightEnzymesFig, ggsave, include = FALSE} 
ggsave(filename = file.path(Figures, "ProchlorococcusLightEnzymes.png"), plot = ProchlorococcusLightEnzymesFig, height = 5, width = 6)
ggsave(filename = file.path(Figures, "S5_Fig.tiff"), plot = ProchlorococcusLightEnzymesFig, height = 5, width = 6, compression = "lzw")
```

>>>>

```{r, assign filepaths, include = FALSE}
DataIn <- file.path("..","Data", "CleanData")
Figures <- file.path("..", "Output", "Figures")
PLOSFiguresRoundX <- file.path("..", "Output", "PLOSFiguresRound1")
# BLAST <- file.path("..", "BLAST")
```

@@

```{r, ProchlorococcusEnzymeKms ggsave, include = FALSE} 
ggsave(filename = file.path(Figures, "ProchlorococcusEnzymeKms.png"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17)
ggsave(filename = file.path(PLOSFiguresRoundX, "Fig11.tiff"), plot = ProchlorococcusEnzymeKms, height = 20, width = 17, compression = "lzw")
```

@@

```{r, DNARepairFig ggsave, include = FALSE} 
ggsave(filename = file.path(Figures, "DNARepairFig.png"), plot = DNARepairFig, height =5 , width = 5)
ggsave(filename = file.path(PLOSFiguresRoundX, "Fig12.tiff"), plot = DNARepairFig, height =5 , width = 5, compression = "lzw")
```

@@

```{r, save ProchlorococcusLightEnzymesFig, ggsave, include = FALSE} 
ggsave(filename = file.path(Figures, "ProchlorococcusLightEnzymes.png"), plot = ProchlorococcusLightEnzymesFig, height = 5, width = 6)
ggsave(filename = file.path(PLOSFiguresRoundX, "S5_Fig.tiff"), plot = ProchlorococcusLightEnzymesFig, height = 5, width = 6, compression = "lzw")
```
